% !TeX root = ../main.tex

\begin{abstract}
  为了提高研究生学位论文质量，统一学位论文的撰写和编辑的格式，便于信息的收集、存储、检索、利用和交流、传播。根据国家有关标准和学校实际，制定本规范。
  
学位论文的定义：学位论文是表明作者从事科学研究取得创造性的结果或有了新的见解，并以此为内容撰写而成、作为提出申请授予相应的学位时评审用的学术论文。

硕士学位论文，要求对所研究的课题有新见解或新成果，并在理论上或实践上对国民经济建设或本门学科发展具有一定的意义，表明作者在本门学科掌握坚实的基础理论和系统的专门知识，具有从事科学研究工作或独立担负专门技术工作的能力。

博士学位论文，要求对所研究的课题在科学上或专门技术上做出创造性成果，并在理论上或实践上对国民经济建设或本门学科发展具有较大的意义，表明作者在本门学科掌握坚实宽广的基础理论和系统深入的专门知识，具有独立从事科学研究工作的能力。

  本文的创新点主要有：
  \begin{itemize}
    \item 用例子来解释模板的使用方法；
    \item 用废话来填充无关紧要的部分；
    \item 一边学习摸索一边编写新代码。
  \end{itemize}

  关键词是为了文献标引工作、用以表示全文主要内容信息的单词或术语。
  关键词不超过 5 个，每个关键词中间用分号分隔。
  英文摘要的关键词与中文摘要的关键词应完全一致。

  \keywords{学位论文，\LaTeX{}，模板}
\end{abstract}
\cleardoublepage
\begin{enabstract}
  An abstract of a dissertation is a summary and extraction of research work
  and contributions.
  Included in an abstract should be description of research topic and research
  objective, brief introduction to methodology and research process, and
  summarization of conclusion and contributions of the research.  An abstract
  should be characterized by independence and clarity and carry identical
  information with the dissertation.
  It should be such that the general idea and major contributions of the
  dissertation are conveyed without reading the dissertation.

  An abstract should be concise and to the point.
  It is a misunderstanding to make an abstract an outline of the dissertation
  and words ``the first chapter'', ``the second chapter'' and the like should
  be avoided in the abstract.

  Key words are terms used in a dissertation for indexing, reflecting core
  information of the dissertation.
  An abstract may contain a maximum of 5 key words, with semi-colons used in
  between to separate one another.

  \enkeywords{Dissertation, \LaTeX{}, template}
\end{enabstract}
